State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-13 prism-backend/research/soa_review/ac.tex
Added review of AKS12. Not really an AC system.

The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}, with the
exception of \cite{cdhk15} that leverages their own signature scheme, called
Unlinkable Randomizable Signatures.

@@

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{aks12}: BBS+-based ACs with revocation.
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\item \cite{cl11}: ACs from aggregate signatures.
\end{itemize}

>>>>

The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}.
\cite{cdhk15} leverages their own signature scheme, called Unlinkable
Randomizable Signatures, which lets users obtain a signature on a set of
(committed) messages and then prove knowledge of (a subset of) these
messages, introducing rerandomization to prevent linking. \cite{fhs19}
follows a similar approach, using vector commitments. Both schemes
\cite{cdhk15,fhs19} seem to be the most efficient AC instantiations to date.
\cite{cdhk15} follows the UC framework; \cite{fhs19} a game-based definition.

@@

The system in \cite{aks12} also uses BBS+ signatures as a main building block
to design a system with accountable anonymity, although it is not ``strictly''
an anonymous credentials system: users receive a credential that lets them
authenticate anonymously against service providers, but this credential does
not include attributes, which seems to be the common case in ACs (however,
with BBS+ it is trivial to add attributes, although this should be modelled).
The main contribution of \cite{aks12} is the design and incorporation of
protocols to block misbehaving users depending on their behaviour, without
relying on trusted third parties. This is based on ``reputation lists'',
maintained by each service provider. Uses that have previously registered
with a Group Manager can authenticate against service providers by proving
knowledge of a valid credential. Depending on how these users behave during
the session with the service provider, the latter adds the interaction to
either a \emph{good behaviour} list, or a \emph{misbehaviour list}. For
subsequent authentications, users prove (in an ``almost unlinkable'' way
w.r.t. previous authentications) that they have a certain reputation,
computed as a weighted sum of their presence in the good/bad behaviour
lists. Moreover, each service provider can maintain multiple thematic lists,
and then require users to satisfy arbitrary boolean policies based on these
lists (e.g., reputation $\gt X_1$ on $list_1$ and reputation $\lt X_2$ on
$list_2$ or reputation $\eq X_3$ on $list_3$) so that only users meeting
the defined policy can access their system. These proves have though a linear
dependency on the number of authentications that each user has done in
the past. To reduce the impact of this, the authors create epochs. When a
user authenticates successfully against a service provider, at a given epoch
$i$, the service provider gives the user a token that authenticates the
reputation that the user had at epoch $i$. Then, when this user tries to
authenticate again, he only needs to give that token, and prove his reputation
since epoch $i$ (this is why authentication is ``almost unlinkable'', as
service providers may learn when the user authenticated for the last time).
Note that no trusted party is involved in the blacklisting process, as
correctness of all tokens exchanged between users and service providers to prove
meeting certain policy, is ensured via the corresponing proof protocols.
Concerning security, the system is proven secure in the simulation paradigm,
claiming to meet (informally defined) properties of:

\begin{itemize}
\item Anonymity: All the SPs can infer from authenticating users is that they
  meet the predefined policy, and that they authenticated at a certain epoch.
\item Authenticity: Only users meeting the defined policies can authenticate.
\item Mis-authentication resistance: Un-registered users cannot authenticate
  successfully.
\item Non-frameability: No coalition of users can cause that another user
  meeting the required policy, cannot authenticate successfully.
\end{itemize}

Somehow, these properties resemble those in the group signatures model in
\cite{kty04}. Probably, the addition of non-frameability is a consequence
of adding a variant of revocation.

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\item \cite{cl11}: ACs from aggregate signatures.
\end{itemize}
